---
title: "Exercises of Chapter 1"
output: html_notebook
---

# First Steps


```{r}
library(tidyverse)
ggplot(data = mpg)
dim(mtcars)
?mpg
ggplot(data = mpg) +
  geom_point(mapping = aes(x = hwy, y = cyl))
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```

Q1: A blank frame.

Q2: `mtcars` has 32 rows and 11 columns.

Q3: the description for `drv`of `mpg` dataset:
> f = front-wheel drive, r = rear wheel drive, 4 = 4wd

Q5: There's no obvious relation between `class` and `drv'.

# Aesthetic Mappings

Q1: 代码含义是按特征 *blue* 设置数据颜色，由于数据 *mpg* 中没有 *blue* 这个特征，
所以所有观测的颜色都被设置为默认的红色。应改为 `... + geom_point(mapping = ..., color = "blue")`.

Q2: Run `str(mpg)`, the features with type `chr` are categorical, that with type `num` or `int` are continuous.

Q3:

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = drv))
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = cty))
```

Q4:

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = drv, shape = drv))
```


Q5:

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), stroke = 1)
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), stroke = 5)
```

`stroke` (笔触，笔画宽度) control the width of the border.

Q6:

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5))
```

当 aesthetic 的值不是变量名称，而是一个表达式时，
按表达式的值（这里是 *True* 和 *False*）对每个观测赋予不同的 aesthetic （这里是颜色）。