---
title: "Data Transformation"
output: html_notebook
---

> Visualisation is an important tool for insight generation, but it is rare that you get the data in exactly the right form you need.

Install `nycflights13` with `install.packages`.

```{r}
library(nycflights13)
library(tidyverse)
flights
```

What is a *tibble*?
How does it different from vanilla *data frame*?

The data type of tibble:

* int
* dbl
* chr
* dttm
* lgl
* fctr
* date

Five key *dplyr* functions:

* filter observations by value: `filter()`
* reorder with `arrange()`
* select feature(s): `select()`
* Create new feature(s) with functions of existing feature(s): `mutate()`
* Collapse many observations down to a single summary: `summarise()`

> These can all be used in conjunction with group_by() which changes the scope of each function from operating on the entire dataset to operating on it group-by-group. These six functions provide the verbs for a language of data manipulation.

上述5个函数与 `group_by()` 组合使用，使前者的作用域从整个 dataset 变为某个分组。

6个函数的使用方法类似：

1. The first argument is a data frame.

1. The subsequent arguments describe what to do with the data frame, using the variable names (without quotes).

1. The result is a new data frame.

# 3.1 Filter

```{r}
jan1 <- filter(flights, month ==1, day ==1)
```

## 3.1.1 Comparisons

`>`, `>=`, `<`, `<=`, `!=` (not equal) and `==`.

Notice `==` is different from `=`, and not using `==` between floating numbers:
```{r}
# filter(flights, month = 1)
sqrt(2) ^ 2 == 2
1 / 49 * 49 == 1
```

# 3.2 Select

```{r}
flt_time <- select(flights, year:day)
flt_time
select(flt_time, day, everything())
```

# 3.6 Summarise

```{r}
by_dest <- group_by(flights, dest)
delay <- summarise(by_dest,
                   count = n(),
                   dist = mean(distance, na.rm = TRUE),
                   delay = mean(arr_delay, na.rm = TRUE))
except_hnl <- filter(delay, count > 20, dest != 'HNL')
ggplot(data = except_hnl, mapping = aes(x = dist, y = delay)) +
  geom_point(aes(size = count), alpha = 1/3) +
  geom_smooth(se = FALSE)
```

