---
title: "Manipulating Strings"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)
library(htmlwidgets)
```

# Matching patterns with regular expressions

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "an")
str_view(x, ".a.")
str_view(c("abc", "a.cd", "bef"), "a\\.c")
```

## Anchors

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "^a")
str_view(x, "a$")
```

## Character classes and alternatives

```{r}
str_view(c("abc", "a.c", "a*c", "a c"), "a[.]c")
str_view(c("abc", "a.c", "a*c", "a c"), ".[*]c")
str_view(c("abc", "a.c", "a*c", "a c"), "a[ ]")
str_view(c("grey", "gray"), "gr(e|a)y")
```

## Repetition

By default these matches are “greedy”: they will match the longest string possible.
You can make them “lazy”, matching the shortest string possible by putting a `?` after them:
```{r}
x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "C{2,3}")
str_view(x, "C{2,3}?")
str_view(x, "C[LX]+")
str_view(x, "C[LX]+?")
```

## Grouping and backreferences

```{r}
str_view(fruit, "(..)\\1", match = TRUE)
```

# Tools

## Detect matches

以 `words` 为例：
```{r}
head(words)
length(words)
```

```{r}
sum(str_detect(words, "^t"))
mean(str_detect(words, "[aeiou]$"))
```

```{r}
xends1 <- words[str_detect(words, "x$")]
xends2 <- str_subset(words, "x$")
identical(xends1, xends2)
```

```{r}
df <- tibble(
  word = words,
  i = seq_along(word)
)
df %>%
  filter(str_detect(word, "x$"))
```

```{r}
df %>%
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )
```

Note that matches never overlap:
```{r}
str_count("abababa", "aba")
str_view_all("abababa", "aba")
```

## Extract matches

